\pkg{partykit}: A Modular Toolkit for Recursive Partytioning in \proglang{R}

### 2015-07-13 pkg/partykit/inst/mloss/mloss2.Rnw
JMLR requests
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@728 255f4249-2263-4417-b1ea-8498779e27a7

%% header declarations
\author{Torsten Hothorn \\ \addr{Universit\"at Z\"urich} \\ \addr{E-mail: Torsten.Hothorn@R-project.org} \AND
        Achim Zeileis \\ \addr{Universit\"at Innsbruck} \\ \addr{E-mail: Achim.Zeileis@R-project.org}}
\title{\pkg{partykit}: A Modular Toolkit for Recursive Partytioning in \proglang{R}}
\editor{Cheng Soon Ong}

@@

\begin{abstract}
  The \proglang{R} package \pkg{partykit} provides a flexible toolkit for
  learning, representing, summarizing, and visualizing a wide range of tree-structured
  regression and classification models. The functionality encompasses: (a)~basic
  infrastructure for \emph{representing} trees (inferred by any algorithm) so that
  unified \code{print}/\code{plot}/\code{predict} methods are available;
  (b)~dedicated methods for trees with \emph{constant fits} in the leaves (or terminal nodes)
  along with suitable coercion functions to create such trees (e.g., by
  \pkg{rpart}, \pkg{RWeka}, PMML); (c)~a reimplementation of \emph{conditional inference
  trees} (\code{ctree}, originally provided in the \pkg{party} package); (d)~an extended
  reimplementation of \emph{model-based recursive partitioning} (\code{mob}, also originally
  in \pkg{party}) along with dedicated methods for trees with parametric models in the
  leaves. Here, a brief overview of the package and its design is given while more detailed
  discussions of items~(a)--(d) are available in vignettes accompanying the package.
\end{abstract}

\begin{keywords}
recursive partitioning, regression trees, classification trees, statistical learning, \proglang{R}.
\end{keywords}

>>>>

\jmlrheading{17}{2015}{1-5}{4/14}{7/15}{Torsten Hothorn and Achim Zeileis}

\ShortHeadings{A Modular Toolkit for Recursive Partytioning}{Hothorn and Zeileis}

%% header declarations
\author{\name Torsten Hothorn \email Torsten.Hothorn@R-project.org \\
        \addr Institut f\"ur Epidemiologie, Biostatistik und Pr\"avention, Universit\"at Z\"urich, Switzerland \\
        \AND
        \name Achim Zeileis \email Achim.Zeileis@R-project.org \\
        \addr Institut f\"ur Statistik, Universit\"at Innsbruck, Austria} 
\title{\pkg{partykit}: A Modular Toolkit for Recursive Partytioning in \proglang{R}}
\editor{Cheng Soon Ong}

@@

\begin{abstract}%
  The \proglang{R} package \pkg{partykit} provides a flexible toolkit for
  learning, representing, summarizing, and visualizing a wide range of tree-structured
  regression and classification models. The functionality encompasses: (a)~basic
  infrastructure for \emph{representing} trees (inferred by any algorithm) so that
  unified \code{print}/\code{plot}/\code{predict} methods are available;
  (b)~dedicated methods for trees with \emph{constant fits} in the leaves (or terminal nodes)
  along with suitable coercion functions to create such trees (e.g., by
  \pkg{rpart}, \pkg{RWeka}, PMML); (c)~a reimplementation of \emph{conditional inference
  trees} (\code{ctree}, originally provided in the \pkg{party} package); (d)~an extended
  reimplementation of \emph{model-based recursive partitioning} (\code{mob}, also originally
  in \pkg{party}) along with dedicated methods for trees with parametric models in the
  leaves. Here, a brief overview of the package and its design is given while more detailed
  discussions of items~(a)--(d) are available in vignettes accompanying the package.
\end{abstract}

\begin{keywords}
recursive partitioning, regression trees, classification trees, statistical learning, \proglang{R}
\end{keywords}
